Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-26 paper/sections/proof-reconstruction.tex
[ paper ] cosmetics for cases equations.

\begin{align}
\begin{split}
\label{eq:unshunt-definition}
&\unshunt_{0}(φ) =\\
&\hspace{3mm}\begin{cases}
\unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃)
  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃)
  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
φ &\text{otherwise.}
\end{cases}
\end{split}
\end{align}

@@

\begin{align}
\label{eq:unshunt-structured}
\begin{split}
&\unshunt_{1}(φ, \zero) = φ\\
&\unshunt_{1}(φ, \suc(n)) =\\
&\hspace{3mm}\begin{cases}
\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n)
  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n) &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
\end{cases}
\end{split}
\end{align}

@@

\begin{equation*}
\label{eq:rank-definition}
rank(φ)=
\begin{cases}
0 &\text{for atomic }φ, \\
rank(φ₁) + c_{¬}  &\text{if } φ ≡ \neg φ₁, \\
\max{(rank(φ₁),rank(φ₂))} + c_{\square}
  &\text{if } φ ≡ φ₁\,\square\, φ₂.
\end{cases}
\end{equation*}

@@

\begin{equation}
\label{eq:unshunt-rank-definition}
\unshunt_{cm}(φ)=
\begin{cases}
\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
0 &\text{otherwise.}
\end{cases}
\end{equation}

@@

\begin{equation}
\label{eq:split-definition}
% \mysplit(φ) =
\begin{cases}
\unshunt(\mysplit(φ₁)) ∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))  & \text{if }φ ≡ φ₁ ∧ φ₂,\\
      &\\[2.5mm]
\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & \text{if }φ ≡ φ₁ ∨ φ₂,\\[2.5mm]

\unshunt(φ₁ ⇒ \mysplit(φ₂))         & \text{if }φ ≡ φ₁ ⇒ φ₂,\\[2.5mm]

\unshunt(φ₁ ⇒ \mysplit(φ₂))         & \text{if }φ ≡ φ₁ ⇔ φ₂,\\
∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁))      &\\[2.5mm]

\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂),\\[2.5mm]
\unshunt(\mysplit(¬ φ₁))            & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂),\\
∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2.5mm]

\unshunt(\mysplit(φ₁))              & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂),\\
∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))    &\\[2.5mm]

\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂),\\
∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))    &\\[2.5mm]

\unshunt(\mysplit(φ₁))              & \text{if }φ ≡ ¬ ¬ φ₁,\\
⊤                                   & \text{if }φ ≡ ¬ ⊥,\\
⊥                                   & \text{if }φ ≡ ¬ ⊤.
\end{cases}
\end{equation}

@@

\begin{align}
  \begin{split}
  conjunct(φ, ψ) =
    \begin{cases}
      ψ &\text{if }φ ≡ ψ,\\
      ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ,\\
      ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ,\\
      φ &\text{otherwise.}
    \end{cases}
  \end{split}
\end{align}

@@

\begin{align}
  \begin{split}
    \label{eq:rdisj-def}
    rdisj(φ) =
    \begin{cases}
    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)) & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃, \\
    φ₁ ∨ rdisj(φ₂)        & \text{if } φ ≡ φ₁ ∨ φ₂, \\
    φ                     & \text{otherwise.}
    \end{cases}
  \end{split}
\end{align}

@@

\begin{equation}
  \begin{split}
  \label{eq:build-or}
  &build_{∨}(φ, ψ) =\\
  &\hspace{3mm}
  \begin{cases}
  ψ &\text{if } φ ≡ ψ,\\
  ψ &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2,\\
  φ &\text{otherwise.}
  \end{cases}
  \end{split}
\end{equation}

@@

\begin{align}
\begin{split}
  \label{eq:factor-definition}
  factor(φ) =
  \begin{cases}
    φ₁ & \text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂),\\
    φ  & \text{otherwise.}
  \end{cases}
\end{split}
\end{align}

@@

\begin{align}
  \begin{split}
  \label{eq:strong-build-or-definition}
    &sbuild_{∨}(φ, ψ) =\\
    &\hspace{3mm}
    \begin{cases}
      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ))  & φ≡ φ₁ ∨ φ₂,\\
      build_{∨}(φ, ψ)  & \text{otherwise.}
    \end{cases}
  \end{split}
\end{align}

@@

\begin{lemma}[lem-reorder$_{∧}$]
  \label{lem:lem-reorder-and}
  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$, where,
  \begin{align*}
      \begin{split}
        reorder_{∧}(φ, ψ) =
        \begin{cases}
          φ &\text{if }φ ≡ ψ, \\
          ψ₁ ∧ ψ₂ &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁,\\
                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂,\\
          φ       &\text{if } ψ ≡ ψ₁ ∧ ψ₂,\\
          conjunct(φ, ψ) &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

\begin{lemma}[lem-conjunct$_{∨}$]
  \label{lem:lem-conjunct-or}
  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
  \begin{align*}
  \begin{split}
    \label{eq:conjunct-or-definition}
    conjunct_{∨}(φ, ψ) =
    \begin{cases}
      ψ &\text{if }reorder_{∨}(φ, ψ) ≡ ψ,\\
      ψ &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) = ψ₁,\\
        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂,\\
      ψ &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ,\\
      ψ &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ,\\
      φ &\text{otherwise.}
    \end{cases}
  \end{split}
  \end{align*}
\end{lemma}

@@

  \begin{align}
      \begin{split}
      reorder_{∧∨}(φ, ψ)=
        \begin{cases}
          ψ &\text{if } φ≡ψ,\\
          ψ &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁,\\
            &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂,\\
          φ &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\\
          conjunct_{∨}(φ, ψ) &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align}
\end{theorem}

@@

\subsubsection{Resolve} % (fold)
\label{ssub:resolve}

@@

\begin{lemma}[lem-rsol]
  \label{lem:lem-rsol}
  $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$, where,
  \begin{align*}
      \begin{split}
        rsol(φ) =
        \begin{cases}
          φ₂ &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄,\\
          φ₂ ∨ φ₄ &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁,\\
          φ &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

@@

\subsubsection{Normal Forms.} % (fold)
\label{ssub:normal_forms}

@@

\begin{lemma}[lem-nnf]
  \label{lem:lem-nnf}
  $Γ ⊢ φ$ then $Γ ⊢ nnf(φ)$, where,
  \begin{align*}
    \begin{split}
    \label{eq:nnf-definition}
    nnf(φ) =
      \begin{cases}
      nnf(φ₁) ∧ nnf(φ₂)
         &\text{if }φ ≡ φ₁ ∧ φ₂, \\
      nnf(φ₁) ∨ nnf(φ₂)
         &\text{if }φ ≡ φ₁ ∨ φ₂, \\
      nnf(¬ φ₁ ∨ φ₂)
         &\text{if }φ ≡ φ₁ ⇒ φ₂, \\
      nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)
         &\text{if }φ ≡ φ₁ ⇔ φ₂, \\
      nnf(¬ φ₁ ∨ ¬ φ₂)
         &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂), \\
      nnf(¬ φ₁ ∧ ¬ φ₂)
         &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂), \\
      nnf(φ₁)
         &\text{if }φ ≡ ¬ ¬ φ₁, \\
      nnf(¬ (φ₂ ∨ ¬ φ₁))
         &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂), \\
      nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁))
         &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂), \\
      ⊥  &\text{if }φ ≡ ¬ ⊤, \\
      ⊤  &\text{if }φ ≡ ¬ ⊥, \\
      φ  & \text{otherwise}.
      \end{cases}
    \end{split}
  \end{align*}
\end{lemma}

\begin{lemma}[lem-dist$_{∨}$]
  \label{lem:lem-dist-or}
  $Γ ⊢ φ$ then $Γ ⊢ dist_{∨}(φ)$, where,
  \begin{align*}
      \begin{split}
      dist_{∨} =
        \begin{cases}
          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃)
            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃,\\
          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃)
            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃),\\
          φ &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

\begin{lemma}[lem-dist]
  \label{lem:lem-dist}
  $Γ ⊢ φ$ then $Γ ⊢ dist(φ)$, where,
  \begin{align*}
      \begin{split}
      dist =
        \begin{cases}
          dist(φ₁) ∧ dist(φ₂)
            &\text{if }φ ≡ φ₁ ∧ φ₂,\\
          dist_{∨}(dist(φ₁) ∨ dist(φ₂))
            &\text{if }φ ≡ φ₁ ∨ φ₂,\\
          φ &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

@@

\subsubsection{Clausification.} % (fold)
\label{ssub:clausification}

\begin{theorem}[thm-clausify] % (fold)
\label{thm:thm_clausify}
  $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
  \begin{align}
      clausify(φ,ψ) =
      \begin{cases}
        ψ, &\text{ if }φ≡ψ\\
        reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
      \end{cases}
  \end{align}
\end{theorem}

>>>>

\begin{align}
\begin{split}
\label{eq:unshunt-definition}
&\unshunt_{0}(φ) =\\
&\hspace{3mm}\begin{cases}
\unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
\unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃),
  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
φ, &\text{otherwise.}
\end{cases}
\end{split}
\end{align}

@@

\begin{align}
\label{eq:unshunt-structured}
\begin{split}
&\unshunt_{1}(φ, \zero) = φ\\
&\unshunt_{1}(φ, \suc(n)) =\\
&\hspace{3mm}\begin{cases}
\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n),
   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
\end{cases}
\end{split}
\end{align}

@@

\begin{equation*}
\label{eq:rank-definition}
rank(φ)=
\begin{cases}
0, &\text{for atomic }φ \\
rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
\max{(rank(φ₁),rank(φ₂))} + c_{\square},
  &\text{if } φ ≡ φ₁\,\square\, φ₂.
\end{cases}
\end{equation*}

@@

\begin{equation}
\label{eq:unshunt-rank-definition}
\unshunt_{cm}(φ)=
\begin{cases}
\unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1,
  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
0, &\text{otherwise.}
\end{cases}
\end{equation}

@@

\begin{equation}
\label{eq:split-definition}
\mysplit(φ) =
\begin{cases}
\unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
\unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
  & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
\unshunt(φ₁ ⇒ \mysplit(φ₂)),
  & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
\unshunt(φ₁ ⇒ \mysplit(φ₂))
  & \text{if }φ ≡ φ₁ ⇔ φ₂\\
∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁)),
  &\\[2.5mm]
\unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
  & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
\unshunt(\mysplit(¬ φ₁))
  & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
  &\\[2.5mm]
\unshunt(\mysplit(φ₁))
  & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
  &\\[2.5mm]
\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
  & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
  &\\[2.5mm]
\unshunt(\mysplit(φ₁)),
  & \text{if }φ ≡ ¬ ¬ φ₁\\
⊤,
  & \text{if }φ ≡ ¬ ⊥\\
⊥,
  & \text{if }φ ≡ ¬ ⊤.
\end{cases}
\end{equation}

@@

\begin{align}
  \begin{split}
  conjunct(φ, ψ) =
    \begin{cases}
      ψ, &\text{if }φ ≡ ψ\\
      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ\\
      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ\\
      φ, &\text{otherwise.}
    \end{cases}
  \end{split}
\end{align}

@@

\begin{align}
  \begin{split}
    \label{eq:rdisj-def}
    rdisj(φ) =
    \begin{cases}
    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
    φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
    φ,                      & \text{otherwise.}
    \end{cases}
  \end{split}
\end{align}

@@

\begin{equation}
  \begin{split}
  \label{eq:build-or}
  &build_{∨}(φ, ψ) =\\
  &\hspace{3mm}
  \begin{cases}
  ψ, &\text{if } φ ≡ ψ\\
  ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
  φ, &\text{otherwise.}
  \end{cases}
  \end{split}
\end{equation}

@@

\begin{align}
\begin{split}
  \label{eq:factor-definition}
  factor(φ) =
  \begin{cases}
    φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
    φ,   &\text{otherwise.}
  \end{cases}
\end{split}
\end{align}

@@

\begin{align}
  \begin{split}
  \label{eq:strong-build-or-definition}
    sbuild_{∨}(φ, ψ) =
    \begin{cases}
      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
      build_{∨}(φ, ψ),  & \text{otherwise.}
    \end{cases}
  \end{split}
\end{align}

@@

\begin{lemma}[lem-reorder$_{∧}$]
  \label{lem:lem-reorder-and}
  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$, where,
  \begin{align*}
      \begin{split}
        reorder_{∧}(φ, ψ) =
        \begin{cases}
          φ, &\text{if }φ ≡ ψ\\
          ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
          φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
          conjunct(φ, ψ) &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

\begin{lemma}[lem-conjunct$_{∨}$]
  \label{lem:lem-conjunct-or}
  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
  \begin{align*}
  \begin{split}
    \label{eq:conjunct-or-definition}
    conjunct_{∨}(φ, ψ) =
    \begin{cases}
      ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) = ψ₁\\
        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
      φ, &\text{otherwise.}
    \end{cases}
  \end{split}
  \end{align*}
\end{lemma}

@@

  \begin{align}
      \begin{split}
      reorder_{∧∨}(φ, ψ)=
        \begin{cases}
          ψ, &\text{if } φ≡ψ\\
          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
             &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
          φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
          conjunct_{∨}(φ, ψ) &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align}
\end{theorem}

@@

\subsubsection{Resolve}
\label{ssub:resolve}

@@

\begin{lemma}[lem-rsol]
  \label{lem:lem-rsol}
  $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$, where,
  \begin{align*}
      \begin{split}
        rsol(φ) =
        \begin{cases}
          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
          φ, &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

@@

\subsubsection{Normal Forms.}
\label{ssub:normal_forms}

@@

\begin{lemma}[lem-nnf]
  \label{lem:lem-nnf}
  $Γ ⊢ φ$ then $Γ ⊢ nnf(φ)$, where,
  \begin{align*}
    \begin{split}
    \label{eq:nnf-definition}
    nnf(φ) =
      \begin{cases}
      nnf(φ₁) ∧ nnf(φ₂),
         &\text{if }φ ≡ φ₁ ∧ φ₂ \\
      nnf(φ₁) ∨ nnf(φ₂),
         &\text{if }φ ≡ φ₁ ∨ φ₂ \\
      nnf(¬ φ₁ ∨ φ₂),
         &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
      nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁),
         &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
      nnf(¬ φ₁ ∨ ¬ φ₂),
         &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂) \\
      nnf(¬ φ₁ ∧ ¬ φ₂),
         &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂) \\
      nnf(φ₁),
         &\text{if }φ ≡ ¬ ¬ φ₁ \\
      nnf(¬ (φ₂ ∨ ¬ φ₁)),
         &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂) \\
      nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)),
         &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂) \\
      ⊥,  &\text{if }φ ≡ ¬ ⊤ \\
      ⊤,  &\text{if }φ ≡ ¬ ⊥ \\
      φ,  & \text{otherwise}.
      \end{cases}
    \end{split}
  \end{align*}
\end{lemma}

\begin{lemma}[lem-dist$_{∨}$]
  \label{lem:lem-dist-or}
  $Γ ⊢ φ$ then $Γ ⊢ dist_{∨}(φ)$, where,
  \begin{align*}
      \begin{split}
      dist_{∨} =
        \begin{cases}
          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
          φ, &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

\begin{lemma}[lem-dist]
  \label{lem:lem-dist}
  $Γ ⊢ φ$ then $Γ ⊢ dist(φ)$, where,
  \begin{align*}
      \begin{split}
      dist =
        \begin{cases}
          dist(φ₁) ∧ dist(φ₂),
            &\text{if }φ ≡ φ₁ ∧ φ₂\\
          dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
            &\text{if }φ ≡ φ₁ ∨ φ₂\\
          φ, &\text{otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{lemma}

@@

\subsubsection{Clausification.}
\label{ssec:clausification}

\begin{theorem}[thm-clausify]
\label{thm:thm_clausify}
  $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
  \begin{align}
      clausify(φ,ψ) =
      \begin{cases}
        ψ, &\text{ if }φ≡ψ\\
        reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
      \end{cases}
  \end{align}
\end{theorem}
